### 2020-01-27 docs/ANE2020/contents.tex
Added results to ANE-2020 tex file.

In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$ used in \eq{eq:balance}. Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime \cite{Smith-1983}. Besides, the net current can be determined from some other expression which is physically or numerically more accurate. Therefore, this new term acts as a correction for the diffusion current. The diffusion current is generally approximated by discretizing Fick's law, and by finite differences, according to
\begin{equation}
  \label{eq:JD}
  \jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
    \frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
\end{equation}
where the diffusion coefficient at the interface is volume-averaged as
\begin{equation}
  \label{eq:Ds}
  D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
{\Delta_i + \Delta_{i+1}}.
\end{equation}
%
About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$. In linearly anisotropic problems, the net current can also be considered to compute the source. Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces. The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
\begin{equation}
  \label{eq:dJ}
  \delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
    \frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
  J_{i+\hzi,g} - \jD_{i+\hzi,g},
\end{equation}
for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary. By retrieving the net current from \eq{eq:dJ} and substitution in \eq{eq:balance} with the source from \eq{eq:qsrc} yields the CMFD balance equation. Finally, using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ} and rearranging, the flux follows by solving a system of linear equations:
%
% Daniele: the signs at superscript are not valid here. This is removed to get shorter text. A sentence is added to the previous paragraph to introduce implicitly the eqn to solove.
%
%The CMFD, eigenvalue balance equation are 
%\begin{equation}
%  \label{eq:CMFD-diff}
%  \begin{gathered}
%  J^+_{D,i+\hzi,g} + \delj^+_{i+\hzi,g} - J^-_{D,i-\hzi,g} - \delj^-_{i-\hzi,g} + \sigma_{i,g}\phi_{i,g}=\\
%  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G\sigma_{s,i,g\leftarrow g'}\phi_{i,g'}.
%  \end{gathered}
%\end{equation}
%Using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ}, and rearranging, yields
\begin{equation}
  \label{eq:CMFD-diff-rearranged}
  \begin{split}
  \left( \frac{-D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_{i-1} + \dx_i}\right) &\phi_{i-1,g} \\
  + \left(\frac{D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} + \frac{D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_i + \dx_{i-1}} + \frac{\sigma_{i,g}}{2}\right) &\phi_{i,g} \\
  + \left( \frac{-D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} \right) &\phi_{i+1,g} = \frac{1}{2}q_{i,g},
  \end{split}
\end{equation}
for $0 < i < I-1$.

@@

% ------------------------------------------
\section{Results}
\label{sec:res}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_I400_RMitr250.pdf}
	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD, RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$). The insets show a zoom-in of the fluxes near the boundary. Results shown here after 250 Ronen iterations and 400 cells.}
	\label{fig:slab-fluxes}		
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($\delta D^+, \delta D^-$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
	\label{fig:slab-RM-corr-factor}
\end{figure}

\begin{figure}[htbp]
	% convergence
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_k_over_I400_RMitr250.pdf}	
	\caption{Convergence of the criticality eigenvalue along 250 Ronen iterations.}
	\label{fig:conv}
\end{figure}

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
	\label{fig:slab-fluxes-dev}
\end{figure}
% ------------------------------------------
\section{Conclusions}
\label{sec:conc}

>>>>

In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$ used in \eq{eq:balance}. Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime \cite{Smith-1983}. Besides, the net current can be determined from some other expression which is physically or numerically more accurate. Therefore, this new term acts as a correction for the diffusion current. The diffusion current is generally approximated by discretizing Fick's law, and by finite differences, according to
\begin{equation}
  \label{eq:JD}
  \jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
    \frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
\end{equation}
where the diffusion coefficient at the interface is volume-averaged as
\begin{equation}
  \label{eq:Ds}
  D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
{\Delta_i + \Delta_{i+1}}.
\end{equation}
%
About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$. % In linearly anisotropic problems, the net current can also be considered to compute the source. <-- pure bullshit ! Can't happen in diffusion.
Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces. The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
\begin{equation}
  \label{eq:dJ}
  \delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
    \frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
  J_{i+\hzi,g} - \jD_{i+\hzi,g},
\end{equation}
for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary. By retrieving the net current from \eq{eq:dJ} and substitution in \eq{eq:balance} with the source from \eq{eq:qsrc} yields the CMFD balance equation. Finally, using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ} and rearranging, the flux follows by solving a system of linear equations:
%
% Daniele: the signs at superscript are not valid here. This is removed to get shorter text. A sentence is added to the previous paragraph to introduce implicitly the eqn to solove.
%
%The CMFD, eigenvalue balance equation are 
%\begin{equation}
%  \label{eq:CMFD-diff}
%  \begin{gathered}
%  J^+_{D,i+\hzi,g} + \delj^+_{i+\hzi,g} - J^-_{D,i-\hzi,g} - \delj^-_{i-\hzi,g} + \sigma_{i,g}\phi_{i,g}=\\
%  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G\sigma_{s,i,g\leftarrow g'}\phi_{i,g'}.
%  \end{gathered}
%\end{equation}
%Using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ}, and rearranging, yields
\begin{equation}
  \label{eq:CMFD-diff-rearranged}
  \begin{split}
  \left( \frac{-D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_{i-1} + \dx_i}\right) &\phi_{i-1,g} \\
  + \left(\frac{D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} + \frac{D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_i + \dx_{i-1}} + \frac{\sigma_{i,g}}{2}\right) &\phi_{i,g} \\
  + \left( \frac{-D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} \right) &\phi_{i+1,g} = \frac{1}{2}q_{i,g},
  \end{split}
\end{equation}
for $0 < i < I-1$.

@@

% ------------------------------------------
\section{Results}
\label{sec:res}
Two test cases are shown in this section. The first is a one-dimensional (1-D) homogeneous plane, representing a typical fuel assembly~\cite{Tomatis-2011}. The second benchmark include three different cores, which are 1-D representation of a Boiling Water Reactor (BWR) configuration~\cite{Rahnema-1997}. Both test cases are calculated and compared by two-group nodal diffusion code (denoted as $D_0$) and the Ronen method (with the implementation of CMFD and pCMFD), and are verified against a discrete ordinates S$_N$ code, with N=16. For all test cases, isotropic scattering are considered. Therefore, the diffusion coefficients for the homogeneous case, calculated by $D_g = (3\sigma_{tr,g})^{-1} = (3\sigma_g)^{-1}$. Void boundary conditions, which are implemented within the diffusion solver, in terms of extrapolated distance for each energy group, and calculated by $d_{ext,g} = 2.13 D_g$. For sake of clarity, the fast and thermal energy groups are denoted by 1 and 2, respectively.

\subsection{Homogeneous case}
\label{sec:homog}
Considering a bare slab of width 21.5 cm, representing a Pressurized Water Reactor (PWR) fuel assembly, homogenized into two energy groups with corresponding cross sections, which are shown in Table~\ref{tab:xs_hom}. Calculations were performed with $I=400$ (No. of cells).

\begin{table}[!htbp]
	\centering
	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] of the homogeneous case~\cite{Tomatis-2011}.}
	\label{tab:xs_hom}
	\begin{tabular}{cccccc}
		%\midrule
		Group $g$ &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
		\midrule
		1 & 5.3115$\times$10\tsup{-1} & 5.04664$\times$10\tsup{-1} & 2.03884$\times$10\tsup{-3} & 1 & 7.15848$\times$10\tsup{-3} \\
		%\midrule
		2 & 1.30058$\times$10\tsup{0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{0}	& 0 & 1.41284$\times$10\tsup{-1} \\
		%\midrule
	\end{tabular}
\end{table}

Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_16$ of the left half slab. The abscissa shows values of the group-dependent neutron mean free path (mfp) $\tau$.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_I400_RMitr250.pdf}
	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD - RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$). The insets show a zoom-in of the fluxes near the boundary. Results shown here after 250 Ronen iterations and 400 cells.}
	\label{fig:slab-fluxes}		
\end{figure}

One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results. On the other hand, closer to the boundary, the Ronen method shows better results. The flux deviations of the left half slab, are shown in Fig.~\ref{fig:flx_err_homg}, calculated by $\Delta\keff = \left(\keff^{-1}-k_{\text{ref}}^{-1}\right)\times 10^5$ pcm.

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
	\label{fig:flx_err_homg}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_rho_I400_RMitr250.pdf}	
	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
	\label{fig:rho_homg}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
	\label{fig:slab-fluxes-dev}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($\delta D^+, \delta D^-$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
	\label{fig:slab-RM-corr-factor}
\end{figure}

% ------------------------------------------
\section{Conclusions}
\label{sec:conc}
